---
title: "Report session"
author:
- name: V. Mhanna, G. Pires, N. Tchitchek, D. Klatzmann, A. Six, E. Mariotti-Ferrandiz
  affiliation: Sorbonne Université, INSERM, Immunology-Immunopathology-Immunotherapy (i3), Paris, France
- name: H. P. Pham
  affiliation: Parean Biotechnologies
runtime: shiny  
output: 
   #html_document
    rmdformats::robobook:
    #toc: true
    toc_depth: 2
    #theme: cerulean
    highlight: tango
    use_bookdown: true
    css: styles.css
---

<style type="text/css">
<!-- div#TOC li { -->
<!--     list-style:none; -->
<!--     background-image:none; -->
<!--     background-repeat:none; -->
<!--     background-position:0;  -->
<!-- } -->
 .book .book-body .page-inner  { 
    max-width: 1400px; 
 <!-- width: 120%;  -->
 } 
 .column-left {
  float: left;
  width: 49.7%;
}
.column-right{
 float: right;
  width: 49.7%;
}
.col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
h1 {
  color: #033c73;
   font-size: 30px;
}
h1.title {
  color: #033c73;
}
h2 {
  color: #033c73;
  font-size: 24px;
}
h3 {
   color: #033c73;
   font-size: 18px;
}
h4 {
   color: #022f5a;
}
h5 {
  color: #033c73;
}
h6 {
   color: #033c73;
}
body{ 
  font-size: 14px;
}
p.caption {
  font-size: 0.9em;
  font-style: italic;
  color: grey;
  margin-right: 10%;
  margin-left: 10%;  
  text-align: justify;
} 
p{
  color: white;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data manipulation

```{r show filtering title, results='asis', echo=FALSE}
if((!is.null(input$filterCountLevel) && !is.null(input$filterCountN) && !is.null(input$filterCountGroup) && input$doFilterCount == 1) ||
   (input$doProductive == 1) ||
   (!is.null(input$dropSampleNames)) || 
   (!is.null(input$publicLevel) && !is.null(input$publicGroup) && input$doPublic == 1) || 
   (!is.null(input$privateLevel) && !is.null(input$privateSingletons) && input$doPrivate == 1) || 
   (!is.null(input$topSeqLevel) && !is.null(input$topSeqGroup) && !is.null(input$topSeqProp) && input$doTopSeq == 1)){cat("## Filtering")}
```


```{r show filter count title, results='asis', echo=FALSE}
if(!is.null(input$filterCountLevel) && !is.null(input$filterCountN) && !is.null(input$filterCountGroup) && input$doFilterCount == 1){cat("**Filter out a repertoire level count**")}
```

```{r rep count, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$filterCountLevel) && !is.null(input$filterCountN) && !is.null(input$filterCountGroup) && input$doFilterCount == 1){
   filterCount(x = RepSeqDT(), level = input$filterCountLevel, n = input$filterCountN, group = input$filterCountGroup)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
      
```


```{r show filter prod title, results='asis', echo=FALSE}
if(input$doProductive == 1){cat("**Filter out unproductive sequences**")}
```

```{r productive, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(input$doProductive == 1){
   getProductive(x = RepSeqDT())
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show drop samples title, results='asis', echo=FALSE}
if(!is.null(input$dropSampleNames)){cat("**Drop a sample**")}
```

```{r drop sample, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$dropSampleNames)){
   dropSamples(x = RepSeqDT(), sampleNames = input$dropSampleNames)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show public title, results='asis', echo=FALSE}
if(!is.null(input$publicLevel) && !is.null(input$publicGroup) && input$doPublic == 1){cat("**Extract shared sequences**")}
```

```{r public, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$publicLevel) && !is.null(input$publicGroup) && input$doPublic == 1){
   getPublic(x = RepSeqDT(), level = input$publicLevel, group = input$publicGroup)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show private title, results='asis', echo=FALSE}
if(!is.null(input$privateLevel) && !is.null(input$privateSingletons) && input$doPrivate == 1){cat("**Extract private sequences**")}
```

```{r private, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$privateLevel) && !is.null(input$privateSingletons) && input$doPrivate == 1){
   getPrivate(x = RepSeqDT(), level = input$privateLevel, singletons = input$privateSingletons)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show topseq title, results='asis', echo=FALSE}
if(!is.null(input$topSeqLevel) && !is.null(input$topSeqGroup) && !is.null(input$topSeqProp) && input$doTopSeq == 1){cat("**Extract top sequences**")}
```

```{r topseq, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$topSeqLevel) && !is.null(input$topSeqGroup) && !is.null(input$topSeqProp) && input$doTopSeq == 1){
   getTopSequences(x=RepSeqDT(), level = input$topSeqLevel, group = input$topSeqGroup, prop = input$topSeqProp)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show normalization title, results='asis', echo=FALSE}
if((!is.null(input$downSampleSize) && !is.null(input$downseed) && !is.null(input$downReplace) && input$doDown == TRUE) ||
   (input$doNorm == TRUE)){cat("## Normalization")}
```


```{r show downsampling title, results='asis', echo=FALSE}
if(!is.null(input$downSampleSize) && !is.null(input$downseed) && !is.null(input$downReplace) && input$doDown == TRUE){cat("**Down-sampling**")}
```

```{r down-sampling, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$downSampleSize) && !is.null(input$downseed) && !is.null(input$downReplace) && input$doDown == TRUE){
   sampleRepSeqExp(x = RepSeqDT(), sample.size = input$downSampleSize, rngseed = isolate(input$downseed), replace = input$downReplace, verbose = FALSE)
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```

```{r show down-sampling, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$DownLevel) && input$doDown == TRUE){
   cts1 <- AnalyzAIRR::assay(RepSeqDT())
        p1 <- histSums(cts1[, sum(count), by=eval(input$DownLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$DownLevel)) +
            ggtitle("Orignial data")+
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        cts2 <- AnalyzAIRR::assay(downSampling())
        p2 <- histSums(cts2[, sum(count), by=eval(input$DownLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$DownLevel)) +
            ggtitle("Downsampled data") +
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))

        gridExtra::grid.arrange(p1, p2, ncol=2)
}
      
```

```{r show down-sampling text entry,echo = FALSE}
if(!is.null(input$DownLevel) && input$doDown == TRUE){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("downText", "Enter text", value="")))
}
```


```{r show shannon title, results='asis', echo=FALSE}
if(input$doNorm == TRUE){cat("**Shannnon-based normalization**")}
```

```{r shannon, echo=FALSE, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(input$doNorm == TRUE){
   ShannonNorm(x = RepSeqDT())
   historydata <- AnalyzAIRR::History(dataFilt())
   knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "center",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```

```{r show shannon, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$NormLevel) && input$doNorm == TRUE){
   cts1 <- AnalyzAIRR::assay(RepSeqDT())
        p1 <- histSums(cts1[, sum(count), by=eval(input$NormLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$NormLevel)) +
            ggtitle("Orignial data")+
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        cts2 <- AnalyzAIRR::assay(shannonNormed())
        p2 <- histSums(cts2[, sum(count), by=eval(input$NormLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$NormLevel)) +
            ggtitle("Shannon normalized data") +
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        
        gridExtra::grid.arrange(p1, p2, ncol=2)
}
      
```

```{r show shannon text entry,echo = FALSE}
if(!is.null(input$NormLevel) && input$doNorm == TRUE){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("shannonText", "Enter text", value="")))
}
```


```{r show Exploratory statistics title, results='asis', echo=FALSE}
if((!is.null(input$plotStats)) || 
   (input$countLevel != "" && !is.null(input$countScale)) || 
   (!is.null(input$plotRare)) ||
   (!is.null(input$divIndex) && input$divLevel != "") || 
   (input$renyiLevel != "") || 
   (input$countIntLevel != "") || 
   (input$rankDistribLevel != "" && input$rankDistribGroupMeth != "")){cat("# Exploratory statistics")}
```


```{r show Basic statistics title, results='asis', echo=FALSE}
if((!is.null(input$plotStats)) || 
   (input$countLevel != "" && !is.null(input$countScale))){cat("## Basic statistics")}
```


```{r show metadata statistics title, results='asis', echo=FALSE}
if(!is.null(input$plotStats)){cat("### Metadata statistics")}
```

```{r metadata stats, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$plotStats)){
   plotStatistics(x=dataFilt(), stat = input$plotStats, groupBy = NULL, label_colors = NULL)
}
      
```

```{r show metadata stats text entry, echo = FALSE}
if(!is.null(input$plotStats)){
  tags$body(style="color: white;",
          p(style="color: white;",
  textInput("metadatastatsText", "Enter text", value="")))
}
```


```{r show Detailed repertoire level statistics title, results='asis', echo=FALSE}
if(input$countLevel != "" && !is.null(input$countScale)){cat("### Detailed repertoire level statistics")}
```

```{r count features, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(input$countLevel != "" && !is.null(input$countScale)){
   countfeatures <- countFeatures(x=dataFilt(), level = input$countLevel, scale = input$countScale, group = NULL)
   knitr::kable(head(countfeatures)) %>%
    kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
    kableExtra::row_spec(0, color="#022f5a", font_size = 12)      
}
      
```

```{r show count features text entry,echo = FALSE}
if(input$countLevel != "" && !is.null(input$countScale)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("countfeaturesText", "Enter text", value="")))
}
```


```{r show Diversity estimation title, results='asis', echo=FALSE}
if((!is.null(input$plotRare)) ||
   (!is.null(input$divIndex) && input$divLevel != "") || 
   (input$renyiLevel != "")){cat("## Diversity estimation ")}
```

```{r show Rarefaction analysis title, results='asis', echo=FALSE}
if(!is.null(input$plotRare)){cat("### Rarefaction analysis")}
```

```{r rarefaction, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$plotRare)){
   plotRarefaction(x=dataFilt(), colorBy = input$plotRare, label_colors = NULL)+ggplot2::theme(legend.position = "right")
}
      
```

```{r show rarefaction text entry,echo = FALSE}
if(!is.null(input$plotRare)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("rarefactionText", "Enter text", value="")))
}
```


```{r rarefaction tab,  echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$plotRare)){
   raretab <- rarefactionTab(x = dataFilt())
   knitr::kable(head(raretab)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```


```{r show Diversity indices title, results='asis', echo=FALSE}
if(!is.null(input$divIndex) && input$divLevel != ""){cat("### Diversity indices")}
```

```{r div ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$divIndex) && input$divLevel != ""){
   plotDiversity(x=dataFilt(), index = input$divIndex, level = input$divLevel, groupBy = NULL, label_colors = NULL)
}
      
```

```{r show div ind text entry,echo = FALSE}
if(!is.null(input$divIndex) && input$divLevel != ""){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("divindText", "Enter text", value="")))
}
```


```{r div ind tab,  echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(input$divLevel != ""){
   divind <- diversityIndices(x=dataFilt(), level = input$divLevel)
   knitr::kable(head(divind)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
      
```


```{r show Renyi index title, results='asis', echo=FALSE}
if(input$renyiLevel != ""){cat("### Renyi index")}
```

```{r renyi ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(input$renyiLevel != ""){
   plotRenyiIndex(x=dataFilt(), level = input$renyiLevel, colorBy = "sample_id", grouped = FALSE, label_colors = NULL)
}
      
```

```{r show renyi ind text entry,echo = FALSE}
if(input$renyiLevel != ""){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("renyiindText", "Enter text", value="")))
}
```


```{r renyi ind tab,  echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(input$renyiLevel != ""){
   renind <- renyiIndex(x=dataFilt(), level = input$renyiLevel)
   knitr::kable(head(renind)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
      
```


```{r show Clonal distribution title, results='asis', echo=FALSE}
if((input$countIntLevel != "") || 
   (input$rankDistribLevel != "" && input$rankDistribGroupMeth != "")){cat("## Clonal distribution")}
```


```{r show Per count interval title, results='asis', echo=FALSE}
if(input$countIntLevel != ""){cat("### Per count interval")}
```

```{r count ind exp, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(input$countIntLevel != ""){
    plotCountIntervals(x=dataFilt(), level = input$countIntLevel, groupBy = NULL, label_colors = NULL)
}
      
```

```{r show count ind exp text entry,echo = FALSE}
if(input$countIntLevel != ""){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("countindexpText", "Enter text", value="")))
}
```


```{r show Per decreasing rank title, results='asis', echo=FALSE}
if(input$rankDistribLevel != "" && input$rankDistribGroupMeth != ""){cat("### Per decreasing rank")}
```

```{r rank distrib exp, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(input$rankDistribLevel != "" && input$rankDistribGroupMeth != ""){
    plotRankDistrib(x = dataFilt(), level = input$rankDistribLevel, scale = input$rankDistribGroupMeth, colorBy = "sample_id", grouped = FALSE, label_colors = NULL)
}
      
```

```{r show rank distrib exp text entry,echo = FALSE}
if(input$rankDistribLevel != "" && input$rankDistribGroupMeth != ""){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("rankdistribexpText", "Enter text", value="")))
}
```


```{r show One-sample analysis title, results='asis', echo=FALSE}
if((!is.null(input$singleSample) && input$indLevel != "") || 
   (!is.null(input$singleSample) && input$indgeneUsageLevel != "" && !is.null(input$singleScale)) || 
   (!is.null(input$singleSample) && input$VJLevel != "" && !is.null(input$singleScale) && !is.null(input$VJProp)) || 
   (!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$singleProp)) || 
   (!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$spectraProp))){cat("# One-sample analysis")}
```


```{r show Clonal distribution per count intervals title, results='asis', echo=FALSE}
if(!is.null(input$singleSample) && input$indLevel != ""){cat("### Clonal distribution per count intervals")}
```

```{r IndCountInt, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$singleSample) && input$indLevel != ""){
   plotIndCountIntervals(x = dataFilt(), sampleName = input$singleSample, level = input$indLevel)
}
      
```

```{r show IndCountInt text entry,echo = FALSE}
if(!is.null(input$singleSample) && input$indLevel != ""){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("IndCountIntText", "Enter text", value="")))
}
```


```{r show V/J usage title, results='asis', echo=FALSE}
if(!is.null(input$singleSample) && input$indgeneUsageLevel != "" && !is.null(input$singleScale)){cat("### V/J usage")}
```

```{r VJUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$singleSample) && input$indgeneUsageLevel != "" && !is.null(input$singleScale)){
   plotIndGeneUsage(x = dataFilt(), sampleName = input$singleSample, level = input$indgeneUsageLevel, scale = input$singleScale)
}
      
```

```{r show VJUsage text entry,echo = FALSE}
if(!is.null(input$singleSample) && input$indgeneUsageLevel != "" && !is.null(input$singleScale)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("VJUsageText", "Enter text", value="")))
}
```


```{r show V-J combination usage title, results='asis', echo=FALSE}
if(!is.null(input$singleSample) && input$VJLevel != "" && !is.null(input$singleScale) && !is.null(input$VJProp)){cat("### V-J combination usage")}
```

```{r VJGeneUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$singleSample) && input$VJLevel != "" && !is.null(input$singleScale) && !is.null(input$VJProp)){
   plotVJusage(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, level = input$VJLevel, prop = input$VJProp) 
}
      
```

```{r show VJGeneUsage text entry,echo = FALSE}
if(!is.null(input$singleSample) && input$VJLevel != "" && !is.null(input$singleScale) && !is.null(input$VJProp)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("VJGeneUsageText", "Enter text", value="")))
}
```


```{r show Stacked spectratyping title, results='asis', echo=FALSE}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$singleProp)){cat("### Stacked spectratyping")}
```

```{r cd3 spectra, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$singleProp)){
   plotSpectratyping(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, prop = input$singleProp)
}
      
```

```{r show cd3 spectra text entry,echo = FALSE}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$singleProp)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("cd3spectraText", "Enter text", value="")))
}
```


```{r show Individual spectratyping title, results='asis', echo=FALSE}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$spectraProp)){cat("### Individual spectratyping")}
```

```{r cd3 spectra ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$spectraProp)){
   plotSpectratypingV(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, prop = input$spectraProp)
}
      
```

```{r show cd3 spectra ind text entry,echo = FALSE}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$spectraProp)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("cd3spectraindText", "Enter text", value="")))
}
```


```{r show Multi-sample analysis title, results='asis', echo=FALSE}
if((!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)) || 
   (!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)) || 
   (!is.null(input$multrenLevel) && !is.null(input$multrenGroup)) || 
   (!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)) || 
   (!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)) || 
   (!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup)) || 
   (!is.null(input$vennLevel) && !is.null(input$vennSamples)) || 
   (!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)) || 
   (!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1) || 
   (!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS)) || 
   (!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)) || 
   (!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup)) || 
   (!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1)){cat("# Multi-sample analysis")}
```


```{r show Comparison of basic statistics title, results='asis', echo=FALSE}
if((!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)) || 
   (!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)) || 
   (!is.null(input$multrenLevel) && !is.null(input$multrenGroup)) || 
   (!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)) || 
   (!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)) || 
   (!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup))){cat("## Comparison of basic statistics")}
```


```{r show Metadata statistics multiple title, results='asis', echo=FALSE}
if(!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)){cat("### Metadata statistics")}
```

```{r stats, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)){
    plotStatistics(x = dataFilt(), stat = input$statisticsStat, groupBy = input$statisticsGroup, label_colors = NULL)
}
      
```

```{r show stats text entry,echo = FALSE}
if(!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("statsText", "Enter text", value="")))
}
```


```{r show Diversity indices multiple title, results='asis', echo=FALSE}
if(!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)){cat("### Diversity indices")}
```

```{r div, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)){
    plotDiversity(x = dataFilt(), level = input$diverLevel, groupBy = input$diverGroup, index = input$diverIndex, label_colors = NULL)
}
     
```

```{r show div text entry,echo = FALSE}
if(!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("divText", "Enter text", value="")))
}
```


```{r show Renyi index multiple title, results='asis', echo=FALSE}
if(!is.null(input$multrenLevel) && !is.null(input$multrenGroup)){cat("### Renyi index")}
```

```{r renyi, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$multrenLevel) && !is.null(input$multrenGroup)){
    plotRenyiIndex(x = dataFilt(), level = input$multrenLevel, colorBy = input$multrenGroup, grouped = TRUE, label_colors = NULL)
}
    
```

```{r show renyi text entry,echo = FALSE}
if(!is.null(input$multrenLevel) && !is.null(input$multrenGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("renyiText", "Enter text", value="")))
}
```


```{r show Count intervals multiple title, results='asis', echo=FALSE}
if(!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)){cat("### Count intervals")}
```

```{r countInt, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)){
    plotCountIntervals(x = dataFilt(), level = input$countIntervalsLevel, groupBy = input$countIntervalsGroup, label_colors = NULL)
}
       
```

```{r show countInt text entry,echo = FALSE}
if(!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("countIntText", "Enter text", value="")))
}
```


```{r show Rank distribution multiple title, results='asis', echo=FALSE}
if(!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)){cat("### Rank distribution")}
```

```{r rankDistrib, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)){
    plotRankDistrib(x = dataFilt(), level = input$multRankLevel, scale = input$multRankScale, colorBy = input$multRankGroup, grouped = TRUE, label_colors = NULL)
}
     
```

```{r show rankDistrib text entry,echo = FALSE}
if(!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("rankDistribText", "Enter text", value="")))
}
```


```{r show V/J usage multiple title, results='asis', echo=FALSE}
if(!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup)){cat("### V/J usage")}
```

```{r geneUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup)){
    plotGeneUsage(x = dataFilt(), level = input$geneUsageLevel, scale = input$geneUsageScale, groupBy = input$geneUsageGroup, label_colors = NULL)
}
    
```

```{r show geneUsage text entry,echo = FALSE}
if(!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("geneUsageText", "Enter text", value="")))
}
```


```{r show Similarity analysis title, results='asis', echo=FALSE}
if((!is.null(input$vennLevel) && !is.null(input$vennSamples)) || 
   (!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)) || 
   (!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1) || 
   (!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS))){cat("## Similarity analysis")}
```


```{r show Repertoire overlap title, results='asis', echo=FALSE}
if(!is.null(input$vennLevel) && !is.null(input$vennSamples)){cat("### Repertoire overlap")}
```

```{r eulerr, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$vennLevel) && !is.null(input$vennSamples)){
    plotEulerr(x = dataFilt(), level = input$vennLevel, sampleNames = input$vennSamples)
}
    
```

```{r show eulerr text entry,echo = FALSE}
if(!is.null(input$vennLevel) && !is.null(input$vennSamples)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("eulerrText", "Enter text", value="")))
}
```


```{r show Repertoire correlation title, results='asis', echo=FALSE}
if(!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)){cat("### Repertoire correlation")}
```

```{r scatter, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)){
    plotScatter(x = dataFilt(), sampleNames = input$scatterUISample, level = input$scatterLevel, scale = input$scatterScale)
}
    
```

```{r show scatter text entry,echo = FALSE}
if(!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("scatterText", "Enter text", value="")))
}
```


```{r show Hierarchical clustering title, results='asis', echo=FALSE}
if(!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1){cat("### Hierarchical clustering")}
```

```{r disHM, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1){
    hm <- plotDissimilarityMatrix(x = dataFilt(), level = input$dissimilarityLevel, method = input$dissimilarityIndex, binary = FALSE, clustering = input$dissimilarityClustering, label_colors = NULL)
    ComplexHeatmap::draw(hm)
}
    
```

```{r show disHM text entry,echo = FALSE}
if(!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("disHMText", "Enter text", value="")))
}
```


```{r show Multidimensional scaling title, results='asis', echo=FALSE}
if(!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS)){cat("### Multidimensional scaling")}
```

```{r MDS, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS)){
    group <- switch((input$grpCol4MDS == "Sample") + 1, input$grpCol4MDS, NULL)
    plotDimReduction(x = dataFilt(), level = input$MDSLevel, method = input$MDSMethod, colorBy = group, label_colors = NULL, dim_method = "MDS")
}
    
```

```{r show MDS text entry,echo = FALSE}
if(!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("MDSText", "Enter text", value="")))
}
```


```{r show Differential analysis title, results='asis', echo=FALSE, fig.width=17, fig.height=6, fig.align='center'}
if((!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)) || 
   (!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup))){cat("## Differential analysis")}
```


```{r show Volcano plot title, results='asis', echo=FALSE}
if(!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)){cat("### Volcano plot")}
```

```{r volcano, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)){
    plotVolcano(x = dataFilt(), level = input$diffLevel, group =  input$diffGroup, FC.TH = input$diffFC, PV.TH = input$diffPV, top = 0)
}
    
```

```{r show volcano text entry,echo = FALSE}
if(!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("volcanoText", "Enter text", value="")))
}
```


```{r diffExpGroup, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$diffGroup) && !is.null(input$diffLevel)){
    diffexp <- diffExpGroup(x = dataFilt(), colGrp = input$diffGroup[[1]], level = input$diffLevel, group = input$diffGroup)
    knitr::kable(head(diffexp)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
    
```


```{r show Principal component analysis title, results='asis', echo=FALSE}
if(!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup)){cat("### Principal component analysis")}
```

```{r PCA, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup)){
    plotDimReduction(x = dataFilt(), level = input$diffPCALevel, method = input$PCAMethod, colorBy = input$diffPCAGroup, label_colors = NULL, dim_method = "PCA")
}
    
```

```{r show PCA text entry,echo = FALSE}
if(!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup)){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("PCAText", "Enter text", value="")))
}
```


```{r show Spectractyping comparison title, results='asis', echo=FALSE}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1){cat("## Spectractyping comparison")}
```

```{r spectratyping comparison HM, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1){
    sampleinfo <- mData(dataFilt())
    ctrnames <- rownames(sampleinfo)[which(sampleinfo[, input$PertGroupSelected] %in% input$CtrlGroup)]
    hm1 <- plotPerturbationScore(x = dataFilt(), ctrl.names = ctrnames, distance = input$pertDist, order = input$pertOrder, label_colors = NULL)
    ComplexHeatmap::draw(hm1)
}
    
```

```{r show spectratyping comparison HM text entry,echo = FALSE}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1){
  tags$body(style="color: white;",
       p(style="color: white;",
  textInput("spectratypingcomparisonHMText", "Enter text", value="")))
}
```


```{r spectratyping comparison table, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, fig.width=17, fig.height=6, fig.align='center'}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1){
    sampleinfo <- mData(dataFilt())
    ctrnames <- rownames(sampleinfo)[which(sampleinfo[, input$PertGroupSelected] %in% input$CtrlGroup)]
    pertscore <- perturbationScore(x = dataFilt(), ctrl.names = ctrnames, distance = input$pertDist, p = 2)
    knitr::kable(head(pertscore)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "center",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
    
```


