---
title: "Report session"
author:
- name: V. Mhanna, G. Pires, N. Tchitchek, D. Klatzmann, A. Six, E. Mariotti-Ferrandiz
  affiliation: Sorbonne Université, INSERM, Immunology-Immunopathology-Immunotherapy (i3), Paris, France
- name: H. P. Pham
  affiliation: Parean Biotechnologies
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file is generated automatically, this is a summary report of your actions on Shiny AnalyzAIRR.

# Data manipulation
## Data extraction

**Assay data**
```{r show assay, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE}

assaydata <- RepSeq::assay(dataFilt())

knitr::kable(head(assaydata)) %>%
    kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
  kableExtra::row_spec(0, color="#022f5a", font_size = 12)      
```

**Metadata**
```{r show metadata, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE}

metadata <- RepSeq::mData(dataFilt())
knitr::kable(head(metadata)) %>%
    kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
  kableExtra::row_spec(0, color="#022f5a", font_size = 12)    
```

**Other data**
```{r show other data, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE}

if(!(is.null(input$otherDataList))){
       otherdata <-  RepSeq::oData(dataFilt())[[input$otherDataList]]
       knitr::kable(head(otherdata)) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "left",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12)    
}
    
      
```

**History data**
```{r show History, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE}

historydata <- RepSeq::History(dataFilt())
knitr::kable(historydata) %>%
        kableExtra::kable_styling(
                        full_width = FALSE,
                        position = "left",
                        font_size = 10) %>%
        kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
```

## Filtering

**Filter out a repertoire level count**
```{r rep count, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$filterCountLevel) && !is.null(input$filterCountN) && !is.null(input$filterCountGroup) && input$doFilterCount == 1){
   filterCount(x = RepSeqDT(), level = input$filterCountLevel, n = input$filterCountN, group = input$filterCountGroup)
}
      
```

**Filter out unproductive sequences**
```{r productive, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(input$doProductive == 1){
   getProductive(x = RepSeqDT())
}
      
```

**Drop a sample**
```{r drop sample, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$dropSampleNames)){
   dropSamples(x = RepSeqDT(), sampleNames = input$dropSampleNames)
}
      
```

**Extract shared sequences**
```{r public, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$publicLevel) && !is.null(input$publicGroup) && input$doPublic == 1){
   getPublic(x = RepSeqDT(), level = input$publicLevel, group = input$publicGroup)
}
      
```

**Extract private sequences**
```{r private, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$privateLevel) && !is.null(input$privateSingletons) && input$doPrivate == 1){
   getPrivate(x = RepSeqDT(), level = input$privateLevel, singletons = input$privateSingletons)
}
      
```

**Extract top sequences**
```{r topseq, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$topSeqLevel) && !is.null(input$topSeqGroup) && !is.null(input$topSeqProp) && input$doTopSeq == 1){
   getTopSequences(x=RepSeqDT(), level = input$topSeqLevel, group = input$topSeqGroup, prop = input$topSeqProp)
}
      
```

## Normalization

**Down-sampling**
```{r down-sampling, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$downSampleSize) && !is.null(input$downseed) && !is.null(input$downReplace) && input$doDown == TRUE){
   sampleRepSeqExp(x = RepSeqDT(), sample.size = input$downSampleSize, rngseed = isolate(input$downseed), replace = input$downReplace, verbose = FALSE)
}
      
```

```{r show down-sampling, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$DownLevel) && input$doDown == TRUE){
   cts1 <- RepSeq::assay(RepSeqDT())
        p1 <- histSums(cts1[, sum(count), by=eval(input$DownLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$DownLevel)) +
            ggtitle("Orignial data")+
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        cts2 <- RepSeq::assay(downSampling())
        p2 <- histSums(cts2[, sum(count), by=eval(input$DownLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$DownLevel)) +
            ggtitle("Downsampled data") +
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))

        gridExtra::grid.arrange(p1, p2, ncol=2)
}
      
```

**Shannnon-based normalization**
```{r shannon, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(input$doNorm == TRUE){
   ShannonNorm(x = RepSeqDT())
}
      
```

```{r show shannon, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$NormLevel) && input$doNorm == TRUE){
   cts1 <- RepSeq::assay(RepSeqDT())
        p1 <- histSums(cts1[, sum(count), by=eval(input$NormLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$NormLevel)) +
            ggtitle("Orignial data")+
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        cts2 <- RepSeq::assay(shannonNormed())
        p2 <- histSums(cts2[, sum(count), by=eval(input$NormLevel)][,V1], xlab="count", ylab=paste0("Number of ", input$NormLevel)) +
            ggtitle("Shannon normalized data") +
            theme_RepSeq()+
            theme(axis.title.x = ggplot2::element_text(size=15),
                  axis.title.y = ggplot2::element_text(size=15),
                  axis.text.x = ggplot2::element_text(size=15),
                  axis.text.y = ggplot2::element_text(size=15))
        
        gridExtra::grid.arrange(p1, p2, ncol=2)
}
      
```

# Exploratory statistics
## Basic statistics

### Metadata statistics

```{r metadata stats, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$plotStats)){
   plotStatistics(x=dataFilt(), stat = input$plotStats, groupBy = NULL, label_colors = NULL)
}
      
```

### Detailed repertoire level statistics
```{r count features, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE}
if(input$countLevel != "" && !is.null(input$countScale)){
   countfeatures <- countFeatures(x=dataFilt(), level = input$countLevel, scale = input$countScale, group = NULL)
   knitr::kable(head(countfeatures)) %>%
    kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
    kableExtra::row_spec(0, color="#022f5a", font_size = 12)      
}
      
```

## Diversity estimation 

### Rarefaction analysis
```{r rarefaction, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6, fig.asp = 1.5}
if(!is.null(input$plotRare)){
   plotRarefaction(x=dataFilt(), colorBy = input$plotRare, label_colors = NULL)+ggplot2::theme(legend.position = "right")
}
      
```

```{r rarefaction tab, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$plotRare)){
   raretab <- rarefactionTab(x = dataFilt())
   knitr::kable(head(raretab)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12)
}
      
```

### Diversity indices
```{r div ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$divIndex) && input$divLevel != ""){
   plotDiversity(x=dataFilt(), index = input$divIndex, level = input$divLevel, groupBy = NULL, label_colors = NULL)
}
      
```

```{r div ind tab, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(input$divLevel != ""){
   divind <- diversityIndices(x=dataFilt(), level = input$divLevel)
   knitr::kable(head(divind)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
      
```

### Renyi index
```{r renyi ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(input$renyiLevel != ""){
   plotRenyiIndex(x=dataFilt(), level = input$renyiLevel, colorBy = "sample_id", grouped = FALSE, label_colors = NULL)
}
      
```


```{r renyi ind tab, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(input$renyiLevel != ""){
   renind <- renyiIndex(x=dataFilt(), level = input$renyiLevel)
   knitr::kable(head(renind)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
      
```

## Clonal distribution

### Per count interval
```{r count ind exp, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(input$countIntLevel != ""){
    plotCountIntervals(x=dataFilt(), level = input$countIntLevel, groupBy = NULL, label_colors = NULL)
}
      
```

### Per decreasing rank
```{r rank distrib exp, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(input$rankDistribLevel != "" && input$rankDistribGroupMeth != ""){
    plotRankDistrib(x = dataFilt(), level = input$rankDistribLevel, scale = input$rankDistribGroupMeth, colorBy = "sample_id", grouped = FALSE, label_colors = NULL)
}
      
```


# One-sample analysis

### Clonal distribution per count intervals
```{r IndCountInt, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$singleSample) && input$indLevel != ""){
   plotIndCountIntervals(x = dataFilt(), sampleName = input$singleSample, level = input$indLevel)
}
      
```

### V/J usage
```{r VJUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$singleSample) && input$indgeneUsageLevel != "" && !is.null(input$singleScale)){
   plotIndGeneUsage(x = dataFilt(), sampleName = input$singleSample, level = input$indgeneUsageLevel, scale = input$singleScale)
}
      
```

### V-J combination usage
```{r VJGeneUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$singleSample) && !is.null(input$VJLevel) && !is.null(input$singleScale) && !is.null(input$VJProp)){
   plotVJusage(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, level = input$VJLevel, prop = input$VJProp) 
}
      
```

### Stacked spectratyping
```{r cd3 spectra, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$singleProp)){
   plotSpectratyping(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, prop = input$singleProp)
}
      
```

### Individual spectratyping
```{r cd3 spectra ind, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$singleSample) && !is.null(input$singleScale) && !is.null(input$spectraProp)){
   plotSpectratypingV(x = dataFilt(), sampleName = input$singleSample, scale = input$singleScale, prop = input$spectraProp)
}
      
```

# Multi-sample analysis

## Comparison of basic statistics

### Metadata statistics
```{r stats, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$statisticsStat) && !is.null(input$statisticsGroup)){
    plotStatistics(x = dataFilt(), stat = input$statisticsStat, groupBy = input$statisticsGroup, label_colors = NULL)
}
      
```

### Diversity indices
```{r div, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$diverLevel) && !is.null(input$diverGroup) && !is.null(input$diverIndex)){
    plotDiversity(x = dataFilt(), level = input$diverLevel, groupBy = input$diverGroup, index = input$diverIndex, label_colors = NULL)
}
     
```

### Renyi index
```{r renyi, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$multrenLevel) && !is.null(input$multrenGroup)){
    plotRenyiIndex(x = dataFilt(), level = input$multrenLevel, colorBy = input$multrenGroup, grouped = TRUE, label_colors = NULL)
}
    
```

### Count intervals
```{r countInt, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$countIntervalsLevel) && !is.null(input$countIntervalsGroup)){
    plotCountIntervals(x = dataFilt(), level = input$countIntervalsLevel, groupBy = input$countIntervalsGroup, label_colors = NULL)
}
       
```

### Rank distribution
```{r rankDistrib, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$multRankLevel) && !is.null(input$multRankScale) && !is.null(input$multRankGroup)){
    plotRankDistrib(x = dataFilt(), level = input$multRankLevel, scale = input$multRankScale, colorBy = input$multRankGroup, grouped = TRUE, label_colors = NULL)
}
     
```

### V/J usage
```{r geneUsage, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$geneUsageLevel) && !is.null(input$geneUsageScale) && !is.null(input$geneUsageGroup)){
    plotGeneUsage(x = dataFilt(), level = input$geneUsageLevel, scale = input$geneUsageScale, groupBy = input$geneUsageGroup, label_colors = NULL)
}
    
```
 
## Similarity analysis

### Repertoire overlap
```{r eulerr, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$vennLevel) && !is.null(input$vennSamples)){
    plotEulerr(x = dataFilt(), level = input$vennLevel, sampleNames = input$vennSamples)
}
    
```

### Repertoire correlation
```{r scatter, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$scatterUISample) && !is.null(input$scatterLevel) && !is.null(input$scatterScale)){
    plotScatter(x = dataFilt(), sampleNames = input$scatterUISample, level = input$scatterLevel, scale = input$scatterScale)
}
    
```

### Hierarchical clustering
```{r disHM, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityLevel) && !is.null(input$dissimilarityIndex) && !is.null(input$dissimilarityClustering) && input$doHm1 == 1){
    hm <- plotDissimilarityMatrix(x = dataFilt(), level = input$dissimilarityLevel, method = input$dissimilarityIndex, binary = FALSE, clustering = input$dissimilarityClustering, label_colors = NULL)
    ComplexHeatmap::draw(hm)
}
    
```

### Multidimensional scaling
```{r MDS, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$MDSLevel) && !is.null(input$MDSMethod) && !is.null(input$grpCol4MDS)){
    group <- switch((input$grpCol4MDS == "Sample") + 1, input$grpCol4MDS, NULL)
    plotDimReduction(x = dataFilt(), level = input$MDSLevel, method = input$MDSMethod, colorBy = group, label_colors = NULL, dim_method = "MDS")
}
    
```


## Differential analysis

### Volcano plot
```{r volcano, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$diffLevel) && !is.null(input$diffGroup) && !is.null(input$diffFC) && !is.null(input$diffPV)){
    plotVolcano(x = dataFilt(), level = input$diffLevel, group =  input$diffGroup, FC.TH = input$diffFC, PV.TH = input$diffPV, top = 0)
}
    
```


```{r diffExpGroup, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$diffGroup) && !is.null(input$diffLevel)){
    diffexp <- diffExpGroup(x = dataFilt(), colGrp = input$diffGroup[[1]], level = input$diffLevel, group = input$diffGroup)
    knitr::kable(head(diffexp)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
    
```

### Principal component analysis
```{r PCA, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$diffPCALevel) && !is.null(input$PCAMethod) && !is.null(input$diffPCAGroup)){
    plotDimReduction(x = dataFilt(), level = input$diffPCALevel, method = input$PCAMethod, colorBy = input$diffPCAGroup, label_colors = NULL, dim_method = "PCA")
}
    
```

## Spectractyping comparison
```{r spectratyping comparison HM, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all', fig.width=12, fig.height=6}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && !is.null(input$pertOrder) && input$doHm == 1){
    sampleinfo <- mData(dataFilt())
    ctrnames <- rownames(sampleinfo)[which(sampleinfo[, input$PertGroupSelected] %in% input$CtrlGroup)]
    hm1 <- plotPerturbationScore(x = dataFilt(), ctrl.names = ctrnames, distance = input$pertDist, order = input$pertOrder, label_colors = NULL)
    ComplexHeatmap::draw(hm1)
}
    
```

```{r spectratyping comparison table, echo=FALSE, warning=FALSE, message=FALSE, error=TRUE, results='hide',fig.keep='all'}
if(!is.null(input$PertGroupSelected) && !is.null(input$CtrlGroup) && !is.null(input$pertDist) && input$doHm == 1){
    sampleinfo <- mData(dataFilt())
    ctrnames <- rownames(sampleinfo)[which(sampleinfo[, input$PertGroupSelected] %in% input$CtrlGroup)]
    pertscore <- perturbationScore(x = dataFilt(), ctrl.names = ctrnames, distance = input$pertDist, p = input$pertPower)
    knitr::kable(head(pertscore)) %>%
            kableExtra::kable_styling(
                    full_width = FALSE,
                    position = "left",
                    font_size = 10) %>%
            kableExtra::row_spec(0, color="#022f5a", font_size = 12) 
}
    
```


